{\fontfamily{ptm}\selectfont A Parameter Free Accelerated Proximal Gradient Method Without Restarting }

### 2024-12-20 Notebook LaTEX/Momentum Accelerations/paper3.tex
>w<, changes

    \cite{nesterov_lectures_2018}
\end{abstract}

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
\noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
\section{Introduction}
    Suppose we are minimizing a differentiable convex function $F$ for simplicity. 
    In addition, assuming the function is $\RR^n$, so it's full domain and $F$ is Lipschitz smooth meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$. 
    \par 
    A good choice of a minimization algorithm is the Nesterov's acceleration schemes that originally proposed in 1983 \cite{nesterov_method_1983}. Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
    \begin{align}
        & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
        \\
        & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
        \\
        & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
        \\
        & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
    \end{align}\label{eqn:example_algorithm}
    It's well known that if the minimizer $x^*$ exists, $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, faster than the gradient descent method which is $\mathcal O(1/k)$, and it's optimal. 
    See Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018}. 
    However, everything is not sunshine and rainbow because the above scheme is associated with an issue. 
    When $F$ is $\mu > 0$ strongly convex, the algorithm oscillates and converges sub-linearly, making it worse than gradient descent. See page 9 of Su et al. \cite{su_differential_2016}. 
    \par
    This issue motivated a vast amount of literatures aims at improving, interpreting, and extending this method. 
    Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
    Beck and Toubelle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it $\mathcal O(1/k^2)$ convergence rate is kept and it performs empirically better. 
    See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm. 
    \par
    Inspired by prior works and the method of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, we present to you firstly, an alternative to restarting that performs well empirically and along with it. 
    Secondly, a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG). 
    The R-WAPG has a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(\theta_t)_{t \ge 1}$. 
    It also has descriptive power to describe several variants of FISTA in the literatures.

    \subsection{Contributions}
        Our contributions are two folds, theoretical and practical. 
        Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
        The choices for $\theta_k$ varies. 
        In Chamboolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ gives strong weak convergence of the iterates $x_k$ in Hilbert space. 
        In Beck \cite{beck_first-order_2017}, it has constant $\theta_t = (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa = \mu/L$. 
        \par
        Firstly, we relaxed the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example_algorithm} and showed an upper bound of the optimal gap. 
        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
        \begin{align*}
            \alpha_0 &\in (0, 1], 
            \\
            \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
            \\
            \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
        \end{align*}
        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
        \begin{align*}
            \mathcal O\left(
                \left(
                    \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
                \right)
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right). 
        \end{align*}
        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces perfectly to the a variant proposed in Chambolle Dossal \cite{chambolle_convergence_2015} and it has the same convergence claim as in the literatures. 
        And when $\rho_k = 1$, R-WAPG reduces perfectly to V-FISTA by Beck \cite{beck_first-order_2017} if $\mu > 0$ and FISTA if $\mu = 0$ and the convergence claim is consistent with the literatures. 
        \par
        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG''. 
        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ with minimal computational cost. 
        We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart. 
    \subsection{Prior works}

@@

\section{Formulation of R-WAPG and its convergence rates}
    The sole focus of this section is Definition \ref{def:wapg}.
    It describes the R-WAPG algorithm which generates iterates $(x_k, y_k, v_k)$ and admits potential convergence claim using Proposition \ref{prop:stepwise-lyapunov}. 
    It introduces the procedures of making the sequence $\alpha_k \in (0, 1)$ which assists with claiming convergence of the algorithm using Proposition \ref{prop:stepwise-lyapunov} by connecting them together. 
    \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}\;\\
        Assume $0 \le \mu < L$. 
        The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge1}$ are valid for R-WAPG all the following holds: 
        \begin{align*}
            \alpha_0 &\in (0, 1], 
            \\
            \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
            \\
            \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
        \end{align*}
        We call $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ the \textbf{R-WAPG Sequences}. 
    \end{definition}
    \begin{observation}\label{obs:r-wapg-observation-1}
        The following is true: 
        \begin{enumerate}
            \item $\rho_k > 0$ for all $k \ge 0$. 
            \item $\forall k \ge 1: L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 +\mu\alpha_k$. 
        \end{enumerate}

@@

@@

@@

        The definition of $R_k$ given is the same as in Proposition \ref{prop:stepwise-lyapunov} hence we can use Proposition \ref{prop:stepwise-lyapunov} to un roll recursively for all $k \ge 1$: 

@@

                F(x_1) - F^* + R_1 + \frac{\gamma_1}{2}\Vert v_1 - x^*\Vert^2

@@

                F(x_1) - F^* + \frac{\gamma_1}{2}\Vert v_1 - x^*\Vert^2

@@

    \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
        Given any initial $(x_1, v_1)$, and a sequence $(\tau_k)_{k \ge 1}, (\xi_k)_{k \ge 1}$ such that for all $k \ge 1$ $\tau_k \in (0, 1), \xi_k \in (0, 1)$. 
        for all $k\ge 1$, iterates $(y_k, z_{k + 1}, x_{k + 1})_{k \ge 1}$ satisfies recursively that: 
        \begin{align*}
            y_k &= (1 + \tau_k)^{-1}(v_k + \tau_k x_k),
            \\
            v_{k + 1} &= (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k,
            \\
            x_{k + 1} &= y_k - L^{-1} g_k. 
        \end{align*}
        If $1 + \xi_k + \tau_k = L\delta_k, \tau_k \neq 0\; \forall k \ge 1$. 
        Then for all $k \ge 1$: 
        $$
            v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k). 
        $$
        Which makes the algorithm a similar triangle form. 
    \end{proposition}
    \begin{proof}
        We are interested in identifying the conditions required for the sequence of $\xi_k, \tau_k, \delta_k$ such that there exists $\theta_k$ satisfying: 
        \begin{align*}
            v_{k + 1} - x_{k + 1} 
            &= \theta_k(x_{k + 1} - x_k).
        \end{align*}
        To verify, do 
        \begin{align*}
            v_{k + 1} &= 
            (1 + \xi_k)^{-1}(v_k + \xi_t y_k - \delta_k \mathcal G_L(y_k))
            \\
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k)y_k - \tau_t x_k + \xi_k y_k - \delta_k \mathcal G_L(y_k))
            \\
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
            \\
            v_{k + 1} - x_{k + 1}
            &= 
            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_t - \tau_k x_k - \delta_t \mathcal G_L(y_k))
            - (y_k - L^{-1}\mathcal G_Ly_k)
            \\
            &= 
            (1 + \xi_k)^{-1}(\tau_ky_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
            + L^{-1}\mathcal G_Ly_k
            \\
            &= 
            (1 + \xi_k)^{-1}
            \left(
                \tau_ty_k - \tau_t x_k + (L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
            \right)
            \\
            &= 
            (1 + \xi_k)^{-1}\tau_k
            \left(
                y_k - x_k + 
                \tau_k^{-1}(L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
            \right).
        \end{align*}
        Going between the first and second inequality we used $v_k = (1 + \tau_k)y_k - \tau_k x_k$ which is rearranged $y_k = (1 + \tau_k)^{-1}(v_k + \tau_k x_k)$. 
        The RHS is can be verified through 
        \begin{align*}
            x_{k + 1} - x_k &= 
            y_t - L^{-1}\mathcal G_L(y_k) - x_k
            \\
            &= (y_k - x_k) - L^{-1}\mathcal G_L(y_k). 
        \end{align*}
        It necessitates the condition: 
        \begin{align*}
            \tau_k^{-1}(L^{-1}(1 + \xi_k) - \delta_k) 
            &= - L^{-1}
            \\
            (1 + \xi_k) - L\delta_k
            &= 
            - \tau_k
            \\
            1 + \xi_k + \tau_k
            &=
            L\delta_k. 
        \end{align*}
        Which allows for: 
        \begin{align*}
            v_{k + 1} - x_{k + 1} &= 
            (1 + \xi_k)^{-1}\tau_t
            \left(y_k - x_k - L^{-1}\mathcal G_L(y_k)\right) 
            = 
            (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k). 
        \end{align*}
    \end{proof}

    \subsection{Narrowing it down}
        \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\
            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}). 
            Then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and for all $k\ge 1$ they are algebraically equivalent to
            \begin{align*}
                & 
                y_{k} = 
                \left(
                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
                \right)^{-1}
                \left(
                    v_{k} + 
                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
                \right), 
                \\
                & x_{k + 1} = 
                y_k - L^{-1} \mathcal G_L y_k, 
                \\
                & v_{k + 1} = 
                \left(
                    1 + \frac{\mu}{L \alpha_k - \mu}
                \right)^{-1}
                \left(
                    v_k + 
                    \left(\frac{\mu}{L \alpha_k - \mu}\right) y_k
                \right) - \frac{1}{L\alpha_{k}}\mathcal G_L y_k. 
            \end{align*}

@@

            For $k = 1, 2, \cdots $, the algorithm generates sequence of vector iterates $(y_{k}, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by: 
        \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\
            Let iterates $(y_k, x_{k}, v_{k})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge 0}$ be given by Definition \ref{def:r-wapg-intermediate}. 
            Then for all $k \ge 1$, iterate $y_k, x_{k + 1}, v_{k + 1}$
            satisfy: 
                x_{k + 1} &= 
                v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 

@@

            From Definition \ref{def:r-wapg-intermediate}, define $(\tau_k, \xi_k, \delta_k)_{k \ge 1}$ in Proposition \ref{prop:abs-st-form} to be
                (\forall k \ge 1) \quad \tau_k &= \frac{L(1 - \alpha_k)}{L\alpha_k - \mu},
                (\forall k \ge 1)\quad 
                \xi_k &= \frac{\mu}{L \alpha_k - \mu},
                (\forall k \ge 1)\quad 
                \delta_k &\defeq \frac{1 + \xi_k}{L\alpha_k}. 
            We claim that these parameters satisfy $L\delta_k = 1 + \tau_k + \xi_k$. 
            To see, we have forall $k\ge 1$: 
                1 + \tau_k + \xi_k &= 
                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 

>>>>

    \todoinline{Write this abstract when finishing. }
\end{abstract}

\noindent{\bfseries 2010 Mathematics Subject Classification:}
Primary 65K10, 90c25, 90C30; Secondary 65Y20. 
\noindent{\bfseries Keywords: } Nesterov acceleration, Proximal point method. 
\section{Introduction}
    Suppose we are minimizing a differentiable convex function $F: \RR^n \rightarrow \RR$ for simplicity. 
    Let $F$ be Lipschitz smooth meaning that there exists $L \in \RR$ such that for all $x \in \RR^n, y\in \RR^n$ it has $\Vert \nabla F(x) - \nabla F(y)\Vert \le L \Vert x - y \Vert$. 
    \par 
    A good choice of a minimization algorithm is the Nesterov's acceleration schemes that originally proposed in 1983 \cite{nesterov_method_1983}. Initialize $x_1 = y_1$ and $t_0 = 1$, the algorithm finds $(x_k)_{k \ge 1}$ for all $k \ge 1$ by: 
    \begin{align}
        & x_{k + 1} = y_k - L^{-1}\nabla F(y_k), 
        \\
        & t_{k + 1} = 1/2\left(1 + \sqrt{1 + 4t_{k}^2}\right), 
        \\
        & \theta_{k + 1} = (t_{k} - 1)/t_{k + 1}, 
        \\
        & y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k). 
    \end{align}\label{eqn:example_algorithm}
    It's well known that if the minimizer $x^*$ exists, $F(x_k) - F(x^*)$ decreases at a rate of $\mathcal O(1/k^2)$, faster than the gradient descent method which is $\mathcal O(1/k)$, and it's optimal. 
    See Chapter 2 of Nesterov's book \cite{nesterov_lectures_2018}. 
    However, everything is not sunshine and rainbow because the above scheme is associated with an issue. 
    When $F$ is $\mu > 0$ strongly convex, the algorithm oscillates and converges sub-linearly, making it worse than gradient descent. See page 9 of Su et al. \cite{su_differential_2016}. 
    \par
    This issue motivated a vast amount of literatures aims at improving, interpreting, and extending this method. 
    Restarting is a popular solution to address the issue of obtaining faster convergence rate when the objective function is strongly convex. 
    Beck and Toubelle \cite{beck_fast_2009} mitigate the issue by restarting and showed that it $\mathcal O(1/k^2)$ convergence rate is kept and it performs empirically better. 
    See \cite{necoara_linear_2019}\cite{aujol_parameter-free_2024} and references within for recent advancements in restarting accelerated proximal gradient algorithm. 
    \par
    Inspired by prior works and the method of Nestrov's estimating sequence \cite{nesterov_lectures_2018}, we present to you firstly, an alternative to restarting that performs well empirically. 
    Secondly, a unified framework of Accelerated Proximal Gradient (APG) which we call Relaxed Weak Accelerated Proximal Gradient (R-WAPG). 
    The R-WAPG has a convergence claim of $F(x_k)- F(x^*)$ for a much more flexible choice of $(\theta_t)_{t \ge 1}$. 
    It also has descriptive power to describe several variants of FISTA in the literatures.

    \subsection{Contributions}
        Our contributions are two folds, theoretical and practical. 
        Nesterov's acceleration extrapolate $y_{k + 1} = x_{k + 1} + \theta_{k + 1}(x_{k + 1} - x_k)$ where $\theta_{k + 1} = (t_{k} - 1)/t_{k + 1} \in (0, 1)$ is the ``momentum''. 
        The choices for $\theta_k$ varies. 
        In Chamboolle, Dossal \cite{chambolle_convergence_2015}, it has $t_k = (n + a - 1)/a$ for all $a > 2$ gives strong weak convergence of the iterates $x_k$ in Hilbert space. 
        In Beck \cite{beck_first-order_2017}, it has constant $\theta_t = (\sqrt{\kappa} - 1)/(\sqrt{\kappa} + 1)$ where $\kappa = \mu/L$. 
        \par
        Firstly, we relaxed the traditional choice of the sequence $\theta_k$ in Equation \ref{eqn:example_algorithm} and showed an upper bound of the optimal gap. 
        Let $(\alpha_k)_{k \ge0}, (\rho_k)_{k \ge 0}$ be two sequences that satisfy
        \begin{align*}
            \alpha_0 &\in (0, 1], 
            \\
            \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
            \\
            \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
        \end{align*}
        Our first main result shows that if $\theta_{k + 1} = (\rho_k\alpha_k(1 - \alpha_k)/(\rho_k\alpha_k^2 + \alpha_{k + 1}))$, using the R-WAPG we proposed in Definition \ref{def:wapg} with Proposition \ref{prop:wagp-convergence}, \ref{prop:r-wapg-momentum-repr}, we can show that the gap $F(x_k) - F(x^*)$ is bounded by:
        \begin{align*}
            \mathcal O\left(
                \left(
                    \prod_{i = 0}^{k - 1} \max(1, \rho_{k})
                \right)
                \prod_{i = 1}^{k} \left(1  - \alpha_i\right)
            \right). 
        \end{align*}
        Our second main result shows that there exists $\rho_k > 1$ such that our R-WAPG reduces perfectly to a variant of FISTA proposed in Chambolle Dossal \cite{chambolle_convergence_2015} with the same convergence claim. 
        And when $\rho_k = 1$, R-WAPG reduces perfectly to V-FISTA by Beck \cite{beck_first-order_2017} if $\mu > 0$ and FISTA if $\mu = 0$ and the convergence claim is consistent with the literatures. 
        \par
        Our practical contribution is an algorithm inspired by a detail in our convergence proof which we call it ``Parameter Free R-WAPG''. 
        The algorithm is parameter free, meaning that it doesn't require knowing $L, \mu$ in advance, and it determines the value of $\theta_t$ by estimating the local concavity using iterates $y_{k}, y_{k + 1}$ with minimal computational cost. 
        We conducted ample amount of numerical experiments to show that it has a favorable convergence rate in practice and behaves similarly to the FISTA with monotone restart. 
    \subsection{Prior works}

@@

\section{Formulation of R-WAPG and its convergence rates}
    The sole focus of this section is Definition \ref{def:wapg}.
    It describes the R-WAPG algorithm which generates iterates $(x_k, y_k, v_k)$ and admits potential convergence claim using Proposition \ref{prop:stepwise-lyapunov}. 
    Definition \ref{def:rwapg-seq} introduces the concept of an R-WAPG sequences which is crucially important. 
    The sequence formulates the R-WAPG algorithm stated in Definition \ref{def:wapg}, it connects the step-wise formulation of R-WAPG (Definition \ref{def:stepwise-wapg}) and describes the convergence claim of R-WAPG in Proposition \ref{prop:wagp-convergence}. 
    In the next section, it continues to play a crucial role in describing several equivalent forms of the R-WAPG algorithm, and their convergence claim. 
    \begin{definition}[R-WAPG sequences]\label{def:rwapg-seq}\;\\
        Assume $0 \le \mu < L$. 
        The sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge1}$ are sequences parameterized by $\mu, L$. 
        They are valid for R-WAPG if all the following holds: 
        \begin{align*}
            \alpha_0 &\in (0, 1], 
            \\
            \alpha_k &\in (\mu/L, 1) \quad (\forall k \ge 1), 
            \\
            \rho_k &:= \frac{\alpha_{k + 1}^2 - (\mu/L)\alpha_{k + 1}}{(1 - \alpha_{k + 1})\alpha_k^2} \quad \forall (k \ge 0). 
        \end{align*}
        We call $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}$ the \textbf{R-WAPG Sequences}. 
    \end{definition}
    \begin{observation}\label{obs:r-wapg-observation-1}
        The following is true: 
        \begin{enumerate}
            \item $\rho_k > 0$ for all $k \ge 0$. 
            \item $\forall k \ge 1: L\alpha_k^2 = (1 - \alpha_k)L\rho_{k - 1}\alpha_{k - 1}^2 +\mu\alpha_k$. 
        \end{enumerate}

@@

        \begin{tcolorbox}
            For $k=1, 2, 3, \cdots$

@@

        \end{tcolorbox}

@@

        The definition of $R_k$ given is the same as in Proposition \ref{prop:stepwise-lyapunov} hence we can use Proposition \ref{prop:stepwise-lyapunov} to unroll recursively for all $k \ge 1$: 

@@

                F(x_1) - F^* + R_1 + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2

@@

                F(x_1) - F^* + \frac{L\alpha_0^2}{2}\Vert v_1 - x^*\Vert^2

@@

    \begin{proposition}[Abstract similar triangle form]\label{prop:abs-st-form}\;\\
        Given any initial $(x_1, v_1)$, and a sequence $(\tau_k)_{k \ge 1}, (\xi_k)_{k \ge 1}$ such that for all $k \ge 1$ $\tau_k \in (0, 1), \xi_k \in (0, 1)$. 
        For all $k\ge 1$, iterates $(y_k, z_{k + 1}, x_{k + 1})_{k \ge 1}$ satisfies recursively that: 
            y_k &= (1 + \tau_k)^{-1}(v_k + \tau_k x_k),
            v_{k + 1} &= (1 + \xi_k)^{-1}(v_k + \xi_k y_k) - (1 + \xi_k)^{-1}\delta_k g_k,
            x_{k + 1} &= y_k - L^{-1} g_k. 
        If $1 + \xi_k + \tau_k = L\delta_k, \tau_k \neq 0\; \forall k \ge 1$. 
        Then for all $k \ge 1$: 
        $$
            v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k). 
        $$
        Which makes the algorithm a similar triangle form. 
        We are interested in identifying the conditions required for the sequence of $\xi_k, \tau_k, \delta_k$ such that there exists $\theta_k$ satisfying: 
            v_{k + 1} - x_{k + 1} 
            &= \theta_k(x_{k + 1} - x_k).
        To verify, do 
            (1 + \xi_k)^{-1}(v_k + \xi_t y_k - \delta_k \mathcal G_L(y_k))
            (1 + \xi_k)^{-1}((1 + \tau_k)y_k - \tau_t x_k + \xi_k y_k - \delta_k \mathcal G_L(y_k))
            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
            v_{k + 1} - x_{k + 1}
            (1 + \xi_k)^{-1}((1 + \tau_k + \xi_k)y_t - \tau_k x_k - \delta_t \mathcal G_L(y_k))
            - (y_k - L^{-1}\mathcal G_Ly_k)
            (1 + \xi_k)^{-1}(\tau_ky_k - \tau_k x_k - \delta_k \mathcal G_L(y_k))
            + L^{-1}\mathcal G_Ly_k
            (1 + \xi_k)^{-1}
                \tau_ty_k - \tau_t x_k + (L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
            (1 + \xi_k)^{-1}\tau_k
                y_k - x_k + 
                \tau_k^{-1}(L^{-1}(1 + \xi_k) - \delta_k) \mathcal G_L(y_k)
        Going between the first and second inequality we used $v_k = (1 + \tau_k)y_k - \tau_k x_k$ which is rearranged $y_k = (1 + \tau_k)^{-1}(v_k + \tau_k x_k)$. 
        The RHS is can be verified through 
            x_{k + 1} - x_k &= 
            y_t - L^{-1}\mathcal G_L(y_k) - x_k
            &= (y_k - x_k) - L^{-1}\mathcal G_L(y_k). 
        It necessitates the condition: 
            \tau_k^{-1}(L^{-1}(1 + \xi_k) - \delta_k) 
            &= - L^{-1}
            (1 + \xi_k) - L\delta_k
            - \tau_k
            1 + \xi_k + \tau_k
            L\delta_k. 
        Which allows for: 
            v_{k + 1} - x_{k + 1} &= 
            (1 + \xi_k)^{-1}\tau_t
            \left(y_k - x_k - L^{-1}\mathcal G_L(y_k)\right) 
            (1 + \xi_k)^{-1}\tau_k(x_{k + 1} - x_k). 
    \subsection{Listing the euivalent representations of R-WAPG}
        This section lists three equivalent representations of the R-WAPG algorithm. 
        They are comparable to existing APG algorithms in the literatures. 
            For $k \ge 1$, the algorithm generates sequence of vector iterates $(y_{k}, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by the procedures: 
            \begin{tcolorbox}
                For $k = 1, 2, \cdots$
            \end{tcolorbox}
            For $k \ge 1$, the algorithm generates sequences of vector iterates $(y_k, v_{k + 1}, x_{k + 1})_{k \ge 1}$ by the procedures: 
            \begin{tcolorbox}
                For $k=1, 2, \cdots $
            \end{tcolorbox}
        \begin{definition}[R-WAPG momentum form]\label{def:r-wapg-momentum-form}
            For any $y_1 = x_1 \in \RR^n$, $(\rho_k)_{k \ge 0}, (\alpha_k)_{k\ge 0}$ given by Definition \ref{def:rwapg-seq}. 
            The algorithm generates iterates $x_{k + 1}, y_{k + 1}$ For $k = 1, 2, \cdots $ by the procedures: 
            \begin{tcolorbox}
                For $k=1, 2,\cdots $
                    & x_{k + 1} = y_k - L^{-1}\mathcal G_Ly_k, 
                    y_{k + 1} = 
                    x_{k + 1} + 
                    \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
            \end{tcolorbox}

            In the special case where $\mu = 0$, the momentum term can be represented without relaxation parameter $\rho_k$: 
            $$
                (\forall k \ge 1)\quad \frac{\rho_k\alpha_k(1 - \alpha_k)}{\rho_k\alpha_k^2 + \alpha_{k + 1}} 
                = \alpha_{k + 1}(\alpha_k^{-1} - 1).  
            $$
        \end{definition}
        \begin{remark}
           \todo[inline]{Consider adding a remark here on how this is similar in format to the Nesterov's accelerated gradient (2.2.19) in his book. }
        \end{remark}

    \subsection{Proving the equivalent representations of R-WAPG}
        \begin{proposition}[First equivalent representation of R-WAPG]\label{prop:wapg-first-equivalent-repr}\;\\
            If the sequence $(y_k, v_k, x_k)_{k \ge 1}$ is produced by R-WAPG (Definition \ref{def:wapg}). 
            Then the iterates can be expressed without $(\gamma_k)_{k \ge1},(\hat \gamma_k)_{k \ge 2}$, and for all $k\ge 1$ they are algebraically equivalent to
                y_{k} = 

@@

        \begin{proposition}[Second equivalent representation of R-WAPG]\label{prop:wagp-st-form}\;\\
            Let iterates $(y_k, x_{k}, v_{k})_{k \ge 1}$ and sequence $(\alpha_k, \rho_k)_{k \ge 0}$ be given by Definition \ref{def:r-wapg-intermediate}. 
            Then for all $k \ge 1$, iterate $y_k, x_{k + 1}, v_{k + 1}$
            satisfy: 
            \begin{align*}
                y_{k} &= 
                \left(
                    1 + \frac{L - L\alpha_{k}}{L\alpha_{k} - \mu}
                \right)^{-1}
                \left(
                    v_{k} + 
                    \left(\frac{L - L\alpha_{k}}{L\alpha_{k} - \mu} \right) x_{k}
                \right), 
                \\
                x_{k + 1} &= 
                y_k - L^{-1} \mathcal G_L y_k, 
                \\
                v_{k + 1} &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
            \end{align*}
        \end{proposition}
        \begin{proof}
            From Definition \ref{def:r-wapg-intermediate}, define $(\tau_k, \xi_k, \delta_k)_{k \ge 1}$ in Proposition \ref{prop:abs-st-form} to be
            \begin{align*}
                (\forall k \ge 1) \quad \tau_k &= \frac{L(1 - \alpha_k)}{L\alpha_k - \mu},
                \\
                (\forall k \ge 1)\quad 
                \xi_k &= \frac{\mu}{L \alpha_k - \mu},
                \\
                (\forall k \ge 1)\quad 
                \delta_k &\defeq \frac{1 + \xi_k}{L\alpha_k}. 
            \end{align*}
            We claim that these parameters satisfy $L\delta_k = 1 + \tau_k + \xi_k$. 
            To see, we have forall $k\ge 1$: 
            \begin{align*}
                1 + \tau_k + \xi_k &= 
                1 + \frac{L(1 - \alpha_k)}{L \alpha_k - \mu} 
                + \frac{\mu}{L \alpha_k - \mu}
                \\
                &= 
                1 + \frac{L - L \alpha_k + \mu}{L\alpha_k - \mu}
                \\
                &= 
                \frac{L - L \alpha_k + \mu + L \alpha_k - \mu}{L\alpha_k - \mu}
                \\
                &= \frac{L}{L\alpha_k - \mu}. 
            \end{align*}
            Next, it also has for all $k \ge 1$: 
            \begin{align*}
                \frac{1 + \xi_k}{\alpha_k}
                &= 
                \frac{1 + \frac{\mu}{L\alpha_k - \mu}}{\alpha_k}
                = 
                \frac{\frac{L\alpha_k - \mu + \mu}{L \alpha_k - \mu}}{\alpha_k}
                = 
                \frac{L}{L\alpha_k - \mu}.
            \end{align*}
            Hence,  $v_{k + 1} - x_{k + 1} = (1 + \xi_k)^{-1}(x_{k + 1} - x_k)\; \forall k \ge 1$ by Proposition \ref{prop:abs-st-form}.
            Therefore, substituting it gives: 
            \begin{align*}
                v_{k + 1} &= 
                x_{k + 1} + \left(
                    1 + \frac{\mu}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= 
                x_{k + 1} + \left(
                    \frac{L\alpha_k}{L\alpha_k - \mu}
                \right)^{-1}\left(
                    \frac{L(1 - \alpha_k)}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= 
                x_{k + 1} + \left(
                    \frac{L\alpha_k - \mu}{L\alpha_k}
                \right)\left(
                    \frac{L - L\alpha_k}{L\alpha_k - \mu}
                \right)(x_{k + 1} - x_k)
                \\
                &= x_{k + 1} + (\alpha_k^{-1} - 1)(x_{k + 1} - x_k). 
            \end{align*}
        \end{proof}

    \begin{proposition}[Third equivalent representation of R-WAPG]\label{prop:r-wapg-momentum-repr}
        \;\\
        Let sequence $(\alpha_k, \rho_k)_{k \ge 0}$ and iterates $(x_k, v_k, y_k)_{k\ge 1}$ given by R-WAPG intermediate form (Definition \ref{def:r-wapg-st-form}). 
        Then for all $k \ge 1$, the iterates $(x_{k + 1}, y_{k + 1})_{k \ge 1}$ are algebraically equivalent to: 
            x_{k + 1} &= y_k - L^{-1}\mathcal G_Ly_k, 
            x_{k + 1} + 
            \frac{\rho_k\alpha_k(1 - \alpha_k)}
            {\rho_k\alpha_k^2 + \alpha_{k + 1}}(x_{k + 1} - x_k). 
        If in addition, $v_1 = x_1$ then 
            y_1 = \left(
                1 + \frac{L - L \alpha_1}{L\alpha_1 - \mu}
                v_1 + \left(
                    \frac{L - L \alpha_1}{L \alpha_1 - \mu}
                \right)x_1
            \right) = x_1. 
        In the special case when $\mu = 0$, the momentum term admits simpler representation 
            (\forall k \ge 1) \quad 
            & = \alpha_{k + 1}(\alpha_k^{-1} - 1). 

@@
